---
title: "School & Unit Dashboard"
output: flexdashboard::flex_dashboard
---

```{r global, include=FALSE}
library(flexdashboard)
knitr::opts_chunk$set(echo = TRUE)
source(here::here("scripts", "avp_dashboard.R"))
```

Beard
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Beard"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Garner
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Garner"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Martin
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Martin"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Pitts
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Pitts"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Peters
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Peters"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Sharp
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Sharp"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Whittenburg
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Whittenburg"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Middleton
===================================== 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fundraiser <- "Middleton"
```

Row
-----------------------------------------------------------------------

### Households in Portfolio

```{r echo=FALSE}
households <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(pm) %>% 
  tally()
valueBox(households$n, icon = "fa-users")
```

### Portfolio Value

```{r echo=FALSE}
portfolio_value <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  summarise(portfolio = sum(rating_value, na.rm = TRUE))
valueBox(dollar(portfolio_value$portfolio), icon = "fa-dollar-sign")
```

Row
-----------------------------------------------------------------------

### Prospects by Geography

```{r echo=FALSE, warning=FALSE}
plot_hex_map(fundraiser)
```

### Portfolio Stats

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
plot_portfolio_stats(fundraiser)
```

Row
-----------------------------------------------------------------------

### Visits - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Visits - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_visit) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_visit == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

Row
-----------------------------------------------------------------------

### Interactions - Within a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Within a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### Interactions - Over a Year

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Over a Year") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Interactions - Never

```{r echo=FALSE, message=FALSE, warning=FALSE}
within_year <- clean_df_constituents %>% 
  filter(pm == fundraiser) %>% 
  group_by(time_since_last_interaction) %>% 
  tally() %>% 
  mutate(pct = (n / sum(n)) * 100) %>% 
  filter(time_since_last_interaction == "Never") %>% 
  select(pct)
gauge(round(within_year$pct, digits = 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```