---
title: 'Week 1: Beachcomber'
author: "Matt Farrow"
date: "8/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

The following are ages of 7 randomly chosen patrons seen leaving the Beach Comber in South Mission Beach at 7pm! We assume that the data come from a normal distribution and would like to test the claim that the mean age of the distribution of Comber patrons is different than 21. Conduct a 6-step hypothesis test to test this claim.  

```{r}
ages <- c(25, 19, 37, 29, 40, 28, 31)
```

## Hypothesis Test

### 1. NULL & Alternative Hypothesis

$H_0: \bar{x} = 21$  
$H_a: \bar{x} ≠ 21$

### 2. Draw and Shade

```{r echo=FALSE}
#' Credit: Volodymyr Orlov
#' modified by MSDS SMU
#' https://github.com/VolodymyrOrlov/MSDS6371/blob/master/shade.r
#' Draws a t-distribution curve and shades rejection regions
#' 
#' @param df degrees of freedom.
#' @param alpha significance level
#' @param h0 null hypothesis value
#' @param sides one of: both, left, right
#' @param t_calc calculated test statistics
#' @examples
#' shade(49, 0.05, 0, t_calc=1.1)
#' shade(91, 0.05, 0, t_calc=NULL, sides = 'right')
#' shade(7, 0.05, 0, t_calc=1.5, sides = 'left')
#' shade(7, 0.05, 0, t_calc=1.5, sides = 'both')

shade <- function(df, alpha, h0 = 0, sides='both', t_calc=NULL) {
  e_alpha = alpha
  if(sides == 'both'){
    e_alpha = alpha / 2
  }
  cv = abs(qt(e_alpha, df))
  curve(dt(x, df), from = -4, to = 4, ylab='P(x)', xaxt='n') 
  abline(v = 0, col = "black", lwd = 0.5)
  labels = h0
  at = 0
  if(sides == 'both' | sides == 'left'){
    x <- seq(-4, -abs(cv), len = 100) 
    y <- dt(x, df)
    polygon(c(x, -abs(cv)), c(y, min(y)), col = "steelblue", border = NA)
    lines(c(-cv, -cv), c(0, dt(-cv, df)), col = "black", lwd = 1)
    text(-cv - (4 - cv) / 2, 0.05, e_alpha)
    labels = c(round(-cv, 3), labels)
    at = c(-cv, at)
  }
  if(sides == 'both' | sides == 'right'){
    x <- seq(abs(cv), 4, len = 100)
    y <- dt(x, df)
    polygon(c(abs(cv), x), c(min(y), y), col = "steelblue", border = NA)
    lines(c(cv, cv), c(0, dt(cv, df)), col = "black", lwd = 1)
    text(cv + (4 - cv) / 2, 0.05, e_alpha)
    labels = c(labels, round(cv, 3))
    at = c(at, cv)
  }
  if(is.numeric(t_calc)){
    abline(v = t_calc, col = "red", lwd = 2)
    text(t_calc + 0.5, 0.2, t_calc, col = "red")
  }
  axis(1, at=at, labels=labels)
}

#The above defines the function shade. To use it, you must call it. More examples are in the comments above.
shade(6, 0.05, 21, sides = "both")
```

```{r}
# Run Two-Sided t-test
t.test(ages, alternative = "two.sided", mu = 21)
```

### 3. t-Value

t = 3.3093

### 4. p-Value

p = 0.01622

### 5. Decision

Reject $H_0$.

### 6. Conclusion

There is sufficient evidence to conclude that the true mean age of patrons at the Beachcomber at 7pm is not equal to 21 (p-value = 0.01622 from a t-test). Because this sample was only drawn at 7pm, the results cannot be applied to the bar at all times.
