---
title: "Live Session 1: CLT"
author: "Matt Farrow"
date: "8/23/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulator to Demonstrate CLT

### Control Parameters
```{r}
df <- read.table(here::here("6306", "week 01", "yob2016.txt"),stringsAsFactors = FALSE,header = FALSE,sep = ";")
n1 <- 10 # sample size per sample for 1st distribution
n2 <- 100 # sample size per sample for 2nd distribution (we will compare these distribuions) 
simulations <- 1000 #number of samples and thus number of xbars we will generate.  
mu <- 0; # mean parameter for use with normal distribuions
sigma <- 1; # standard deviation parameter for use with normal distribuions
```

### Data Holder
```{r}
xbar_holder1 <- numeric(simulations) # This will hold all the sample means for the first distribution.
xbar_holder2 <- numeric(simulations) # This will hold all the sample means for the second distribution.
```

### Simulate and Store
Generate 1000 samples each of size 10 and find the mean of each sample.  Then store each mean in the xbar_holder vector.

```{r}
for (i in 1:simulations)
{ 
  sample1 <- rnorm(n1,mean = mu, sd = sigma)
  sample2 <- rnorm(n2,mean = mu, sd = sigma)
  xbar1 <- mean(sample1)
  xbar2 <- mean(sample2)
  xbar_holder1[i] <- xbar1
  xbar_holder2[i] <- xbar2
}
```

### Display the Distribution of Sample Means (plot a histogram of the sample means)
```{r}
par(mfrow = c(2,1))
hist(xbar_holder1, col = "blue", main = paste("Distribution of the sample mean: n = ", n1), xlab = "Dist 1 Sample Means", xlim = c(-4,4))
hist(xbar_holder2, col = "red", main = paste("Distribution of the sample mean: n = ", n2), xlab = "Dist 2 Sample Means", xlim = c(-4,4))
```

### Summary Statistics of the Distribution of the Simulated Sample Means
```{r}
summary(xbar_holder1) #5 number summary and the mean
summary(xbar_holder2) #5 number summary and the mean
sd(xbar_holder1) # standard deviation of dstribuion 1
sd(xbar_holder2) #standard deviation of distribuion 2
```

## For Live Session

*Adapt the code to generate a population of 10,000,000 from a chi-square distribution with 2 degrees of freedom. This is a heavily right skewed distribution.  (Hint: rchisq()).  You will have to read up on this function and probably do some trial and error. Being able to learn new functions and methods is a key skill.*

```{r}
pop <- rchisq(10000000, 2)
```

### Histogram of the Population

```{r}
hist(pop, main = "Distribution of Population", 
     xlab = "Population", 
     ylab = "Frequency")
```

### Mean and Standard Deviation

```{r}
mean(pop)
sd(pop)
```

### Central Limit Theorem

According to the central limit theorem, what should be the approximate distribution of sample means of size 50 from this right skewed population?  **Based on the Central Limit Theorem, the approximate distribution of sample means should be a normal distribution.**

What should be the mean and standard error of the mean (standard deviation of the distribution of sample means)? **The mean should be 0 and the standard error of the mean should be 1.**

Now let’s check this: Adapt the CLT code to draw 10,000 means each of size 50 from this population and provide the sampling distribution of this sample mean.  Provide a histogram of these 10,000 sample means.

### Setup
```{r}
# Sample Size
n <- 50

# Number of Samples (and thus number of $\bar{x})$)
simulations <- 10000

# Mean Parameter for Normal Distributions
mu <- 0

# Standard Deviation for Normal Distributions
sigma <- 1

# Data Holder
xbar_holder <- numeric(simulations)
```

### Simulate and Store

Generate 10,000 samples each of size 50 and find the mean of each sample. Then store each mean in the xbar_holder vector.

```{r}
for (i in 1:simulations)
{ 
  sample <- rnorm(n,mean = mu, sd = sigma)
  xbar <- mean(sample)
  xbar_holder[i] <- xbar
}
```

### Display the Distribution of Sample Means (plot a histogram of the sample means)
```{r}
par(mfrow = c(2,1))
hist(xbar_holder,
     main = paste("Distribution of the Sample Mean: n = ", n), 
     xlab = "Dist 1 Sample Means", xlim = c(-4,4))
```

### Summary Statistics of the Distribution of the Simulated Sample Means
```{r}
summary(xbar_holder)
sd(xbar_holder)
```